Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-08-01 article_springer/article_springer.Rmd
Exponential  --> exponential (uniformly)
Add missing Acknowledgments.

*Proof of Theorem:* 	Due to assumption \eqref{assumptionJs}
\begin{align*}
& & P\left(\frac{J_1 \vee \ldots \vee J_{\lfloor c \rfloor}-d(c)}{a(c)} \leq x\right) & \rightarrow F(x;\xi) \\
& \Longleftrightarrow & F_J(xa(c)+d(c))^{\lfloor c \rfloor} & \rightarrow F(x;\xi) \\
& \Longleftrightarrow &  \lfloor c \rfloor \log F_J(\ell_c) & \rightarrow \log F(x;\xi)
\end{align*}
as $c \rightarrow \infty$, for any $x$ from 
the support of $F(x;\xi)$,	with $\ell_c:=xa(c)+d(c)$. Furthermore, since $\log(1-x) \sim -x$ for small $x$ it follows
$$
c \cdot p(\ell_c) \rightarrow -\log F(x;\xi) \quad  \text{ as } c \rightarrow \infty,
$$
with $p(\ell_c):= 1-F(\ell_c)$. Due to $\tau(\ell_c) \sim {\rm Geo}(p(\ell_c))$ and above equation,
	it follows that $\tau(\ell_c)/c$ converges to an Exponential random variable,
$$
	\frac{\tau(\ell_c)}{c} \Rightarrow E \quad  \text{ as } c \rightarrow \infty
$$
	 with inverse mean $\lambda:=-\log F(x;\xi)$. Due to
$$
	S(c):= \sum_{i=1}^{\lfloor c \rfloor} \frac{W_i}{b(c)} \Rightarrow D \quad \text{ as } c \rightarrow \infty,
$$
    it follows with Gnedenko's transfer theorem (see @gnedenko1983limit), that
$$
	\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(\ell_c)}  \Rightarrow Z \quad \text{ as }  c \rightarrow \infty, 
$$
	where the distribution of $Z$ has the characteristic function
\begin{align*}
\Psi(s) &= \int_0^{\infty} (\Phi_D(s))^{y} F_E(dy) = \frac{1}{1-\log(\Phi_D(s))/\lambda}\\
&= \frac{1}{1+s^{\beta}\lambda^{-1}} = \frac{1}{1+(s \lambda^{-1/\beta})^{\beta}}
\end{align*}
    where $\Phi_D(s) = \exp(-s^\beta)$ is the Laplace transform of $D$ 
    and  $F_E(dy)$ is the distribution function of $E$. Hence, $Z$ is Mittag-Leffler distributed with scale parameter $\lambda^{-1/\beta}$. Rewriting
$$
    \sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(1/p(\ell_c))} = \left(\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(c) }\right) \frac{b(c)}{b(1/p(\ell_c))}  
$$
	and
$$
	\frac{b(c)}{b(1/p(\ell_c))} = \frac{b(c)}{b(c/(p(\ell_c)c))} \sim (p(\ell_c) \cdot c)^{1/\beta} \rightarrow \lambda^{1/\beta} \text{ as } c \rightarrow \infty,
$$
	the second factor converges to $\lambda^{1/\beta}$, and it follows that
	 $Z \sim {\rm ML}(\beta,1)$. Since $c \rightarrow \infty$ is equivalent to $\ell \uparrow x_R$, the assertion follows with $\ell:=\ell_c$ and $p_\ell:=p(\ell_c)$.
\qed

@@

The authors would like to thank Prof. Peter Scheffler for insights on stochastic process limits for CTRMs, Prof. Roland Fried for discussion regarding the statistical methods and Gurtek Gill who helped create the MittagLeffleR R-package.

>>>>

*Proof of Theorem:* 	Due to assumption \eqref{assumptionJs}
\begin{align*}
& & P\left(\frac{J_1 \vee \ldots \vee J_{\lfloor c \rfloor}-d(c)}{a(c)} \leq x\right) & \rightarrow F(x;\xi) \\
& \Longleftrightarrow & F_J(xa(c)+d(c))^{\lfloor c \rfloor} & \rightarrow F(x;\xi) \\
& \Longleftrightarrow &  \lfloor c \rfloor \log F_J(\ell_c) & \rightarrow \log F(x;\xi)
\end{align*}
as $c \rightarrow \infty$, for any $x$ from 
the support of $F(x;\xi)$,	with $\ell_c:=xa(c)+d(c)$. Furthermore, since $\log(1-x) \sim -x$ for small $x$ it follows
$$
c \cdot p(\ell_c) \rightarrow -\log F(x;\xi) \quad  \text{ as } c \rightarrow \infty,
$$
with $p(\ell_c):= 1-F(\ell_c)$. Due to $\tau(\ell_c) \sim {\rm Geo}(p(\ell_c))$ and above equation,
	it follows that $\tau(\ell_c)/c$ converges to an exponential random variable,
$$
	\frac{\tau(\ell_c)}{c} \Rightarrow E \quad  \text{ as } c \rightarrow \infty
$$
	 with inverse mean $\lambda:=-\log F(x;\xi)$. Due to
$$
	S(c):= \sum_{i=1}^{\lfloor c \rfloor} \frac{W_i}{b(c)} \Rightarrow D \quad \text{ as } c \rightarrow \infty,
$$
    it follows with Gnedenko's transfer theorem (see @gnedenko1983limit), that
$$
	\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(\ell_c)}  \Rightarrow Z \quad \text{ as }  c \rightarrow \infty, 
$$
	where the distribution of $Z$ has the characteristic function
\begin{align*}
\Psi(s) &= \int_0^{\infty} (\Phi_D(s))^{y} F_E(dy) = \frac{1}{1-\log(\Phi_D(s))/\lambda}\\
&= \frac{1}{1+s^{\beta}\lambda^{-1}} = \frac{1}{1+(s \lambda^{-1/\beta})^{\beta}}
\end{align*}
    where $\Phi_D(s) = \exp(-s^\beta)$ is the Laplace transform of $D$ 
    and  $F_E(dy)$ is the distribution function of $E$. Hence, $Z$ is Mittag-Leffler distributed with scale parameter $\lambda^{-1/\beta}$. Rewriting
$$
    \sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(1/p(\ell_c))} = \left(\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(c) }\right) \frac{b(c)}{b(1/p(\ell_c))}  
$$
	and
$$
	\frac{b(c)}{b(1/p(\ell_c))} = \frac{b(c)}{b(c/(p(\ell_c)c))} \sim (p(\ell_c) \cdot c)^{1/\beta} \rightarrow \lambda^{1/\beta} \text{ as } c \rightarrow \infty,
$$
	the second factor converges to $\lambda^{1/\beta}$, and it follows that
	 $Z \sim {\rm ML}(\beta,1)$. Since $c \rightarrow \infty$ is equivalent to $\ell \uparrow x_R$, the assertion follows with $\ell:=\ell_c$ and $p_\ell:=p(\ell_c)$.
\qed

@@

The authors would like to thank Prof. Peter Scheffler for insights on 
stochastic process limits for CTRMs, Prof. Roland Fried for discussion 
regarding the statistical methods and Gurtek Gill who helped create the 
MittagLeffleR R-package. Peter Straka was supported by the Discovery 
Early Career Research Award DE160101147 on the Project 
“Predicting Extremes when Events Occurin Bursts” by 
the Australian Research Council. Katharina Hees was 
supported by the DAAD co-financed by the 
German Federal Ministry of Education andResearch (BMBF)
